\documentclass[12pt,a4paper]{article}
\usepackage[a4paper,margin=1.8cm]{geometry}
\usepackage{fontspec}
\usepackage{polyglossia}
\setmainlanguage{english}
\setotherlanguage{hebrew}
\setmainfont{Times New Roman}
\newfontfamily\hebrewfont{Arial}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{listings}
\lstset{basicstyle=\ttfamily\small,breaklines=true,columns=fullflexible}
\pagestyle{fancy}
\setlength{\headheight}{15pt}
\fancyhf{}
\fancyhead[L]{Production-Ready AI Agents}
\fancyhead[R]{CrewAI and LaTeX Research Article}
\fancyfoot[C]{\thepage}
\setstretch{1.18}
\setlength{\parindent}{1.25em}
\setlength{\parskip}{0pt}
\setlist{nosep}
\emergencystretch=2em
\sloppy
\titleformat{\section}{\Large\bfseries}{\thesection.}{0.55em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection.}{0.5em}{}
\begin{document}
\thispagestyle{empty}
\begin{center}
\vspace*{3.5cm}
{\Huge\bfseries "AI Agents for Early Detection of Mental Health Crises Using Multimodal Data"\par}
\vspace{0.7cm}
{\Large From Prompt Demos to Governed Runtime Systems\par}
\vspace{1.4cm}
{\Large Aisha Abu Dahesh and Yousef Asadi\par}
\vspace{0.5cm}
{\large Orchestration of AI Agents -- Assignment 03\par}
{\large Lecturer: Dr. Yoram Segal\par}
\vfill
{\large University of Haifa\par}
{\large June 2026\par}
\end{center}
\clearpage
\section*{Abstract}
Production AI agents are moving from demonstrations toward governed runtime systems that must plan, use tools, preserve evidence, respect security boundaries, and produce artifacts that can be inspected by humans. This article is generated by an online CrewAI crew and rendered through LaTeX. The generation workflow assigns planning, research, writing, LaTeX engineering, and quality assurance to separate agents before compiling the final PDF.

\textbf{Keywords:} AI agents, CrewAI, LaTeX, production readiness, orchestration, observability, BiDi text.
\clearpage
\input{chapters/online_article}
\begin{thebibliography}{20}
\bibitem{openai2025agents} OpenAI. Agentic application and tool-use documentation, 2025--2026.
\bibitem{google2026gemini} Google. Gemini API and agentic generation documentation, 2026.
\bibitem{pmlr2025agentsecurity} Research literature on agent security and prompt injection, 2025.
\bibitem{ieee2026observability} IEEE and industry literature on AI observability, 2026.
\bibitem{acm2026adaptability} ACM literature on adaptive AI systems, 2026.
\bibitem{crewai2026docs} CrewAI documentation: agents, tasks, crews, and process concepts, 2026.
\bibitem{langchain2025roadmap} LangChain and LangGraph documentation, 2025--2026.
\bibitem{microsoft2026copilot} Microsoft Copilot and agent infrastructure references, 2026.
\bibitem{mlops2026handbook} MLOps and production deployment handbooks for AI systems, 2026.
\bibitem{nist2023airmf} NIST. AI Risk Management Framework, 2023.
\bibitem{owasp2025llm} OWASP. Top 10 for Large Language Model Applications, 2025.
\bibitem{anthropic2025mcp} Anthropic. Model Context Protocol documentation, 2025--2026.
\bibitem{google2025a2a} Google. Agent2Agent protocol documentation, 2025--2026.
\bibitem{openai2026evals} OpenAI. Evaluation and safety guidance for agentic systems, 2026.
\bibitem{crew2026enterprise} CrewAI. Enterprise agent orchestration patterns, 2026.
\bibitem{langchain2026agents} LangChain. Agent, tool, and retrieval documentation, 2026.
\bibitem{arxiv2025memory} Recent research on memory poisoning and long-context agent risks, 2025.
\bibitem{arxiv2025toollearning} Recent research on tool learning and API-using agents, 2025.
\bibitem{arxiv2026codingagents} Recent research on prompt injection against coding agents, 2026.
\bibitem{iso2025ai} ISO/IEC guidance on AI governance and system quality, 2025.
\end{thebibliography}
\end{document}
